Convolutional equivalent layer for gravity data processing

### 2020-04-29 manuscript/figures.tex
include new figures for tests with synthetic data

\plot{Figure5}{width=13.5cm}{
	{Application to synthetic data. 
	Noise-corrupted gravity data (in color map) produced by three synthetic sources: 
	a sphere with density contrast $-0.5\, \mathrm{g/cm^3}$ and 
	two rectangular prisms with density contrasts $0.35\, \mathrm{g/cm^3}$ (upper-left body) and 
	$0.4\, \mathrm{g/cm^3}$ (upper-right body). The black lines represent the horizontal projection 
	of the sources.}
	\label{fig:synthetic_data}
}

\plot{Figure678_r1}{width=6cm}{
	{Application to synthetic data. 
	(a) Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by the fast equivalent-layer technique \citep{siqueira-etal2017}. 
	The mean and standard deviation are $8.264 \times 10^{-7}$ and $0.0144$ mGal, respectively.
	(b) Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by our method. The mean and standard deviation are 
	$8.264 \times 10^{-7}$ and $0.0144$ mGal, respectively.
	(c) Difference between the predicted data produced by the fast equivalent-layer technique 
	and our method.}
	\label{fig:comparison_datafits}
}

\plot{Figure10_r1}{width=6cm}{
	{Application to synthetic data.
	(a) Gravity data produced by the synthetic sources at $z = -300$ m.
	(b) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $-0.0003$ mGal and standard deviation $0.0124$ mGal. 
	(c) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with our method (not shown), with mean $-0.0003$ mGal and 
	standard deviation $0.0124$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.62026$ and $0.00834$ seconds, respectively.}
	\label{fig:upward_comparison}
}

\plot{Figure11_r1}{width=6cm}{
	{Application to synthetic data. 
	(a) Gravity data produced by the synthetic sources at $z = -50$ m.
	(b) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $0.0001$ mGal and standard deviation $0.0079$ mGal. 
	(c) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with our method (not shown), with mean $0.0001$ mGal and 
	standard deviation $0.0079$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.59654$ and $0.00547$ seconds, respectively.}
	\label{fig:downward_comparison}
}

>>>>

\plot{synthetic_data_med}{width=13.5cm}{
	{Application to synthetic data. 
	Noise-corrupted gravity data (in color map) produced by three synthetic sources: 
	a sphere with density contrast $-1.25\, \mathrm{g/cm^3}$ and 
	two rectangular prisms with density contrasts $1.00\, \mathrm{g/cm^3}$ (upper-left body) and 
	$1.30\, \mathrm{g/cm^3}$ (upper-right body). 
	The synthetic data are contaminated with a pseudorandom Gaussian noise having null mean 
	and standard deviation equal to $0.1 \, \mathrm{mGal}$.
	The black lines represent the horizontal projection of the sources.}
	\label{fig:synthetic_data}
}

\plot{deltas_gz_med}{width=6cm}{
	{Application to synthetic data. 
	(a) Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by the fast equivalent-layer technique \citep{siqueira-etal2017}. 
	(b) Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by our method. 
	The mean ($-4.493 \times 10^{-5}$ mGal) and standard deviation ($0.093$ mGal) for residuals
	shown in a and b are exactly the same.
	(c) Difference between the predicted data produced by the fast equivalent-layer technique 
	and our method.
	The computation times spent by the fast equivalent-layer technique and 
	our method were $10.996$ and $0.428$ seconds, respectively.}
	\label{fig:comparison_datafits}
}

\plot{upward_fourier_med}{width=13.5cm}{
	{Application to synthetic data.
	(a) Gravity data produced by the synthetic sources at $z = -300$ m.
	(b) Residuals between the data shown in a and the upward-continued 
	data obtained with our method (not shown), with 
	mean $0.003$ mGal and standard deviation $0.034$ mGal. 
	(c) Residuals between the data shown in a and the upward-continued 
	data obtained with the fast equivalent-layer technique (not shown), with 
	mean $0.003$ mGal and standard deviation $0.034$ mGal.
	(d) Residuals between the data shown in a and the upward-continued 
	data obtained with the classical Fourier approach (not shown), with 
	mean $-0.030$ mGal and standard deviation $0.262$ mGal.
	The residuals shown in b, c and d have the same scale. 	 
	The computation times spent by the fast equivalent-layer technique and 
	our method were $8.697$ and $0.005$ seconds, respectively.}
	\label{fig:upward_comparison}
}

\plot{downward_fourier_med}{width=13.5cm}{
	{Application to synthetic data. 
	(a) Gravity data produced by the synthetic sources at $z = -50$ m.
	(b) Residuals between the data shown in a and the downward-continued 
	data obtained with our method (not shown), with 
	mean $-0.001$ mGal and standard deviation $0.038$ mGal. 
	(c) Residuals between the data shown in a and the downward-continued 
	data obtained with the fast equivalent-layer technique (not shown), with 
	mean $-0.001$ mGal and standard deviation $0.038$ mGal.
	(d) Residuals between the data shown in a and the downward-continued 
	data obtained with the classical Fourier approach (not shown), with 
	mean $-0.030$ mGal and standard deviation $0.262$ mGal.
	The residuals shown in b, c and d have the same scale.	 
	The computation times spent by the fast equivalent-layer technique and 
	our method were $8.795$ and $0.004$ seconds, respectively.}
	\label{fig:downward_comparison}
}

### 2020-04-29 manuscript/synthetic_data.tex
include new figures for tests with synthetic data

We simulated three sources whose horizontal projections are shown in Figure \ref{fig:synthetic_data} as black lines. 
These sources are a sphere with radius of $1\,000$ m with density contrast of 
$-0.5\, \mathrm{g/cm^3}$ and two rectangular prisms with density contrasts of $0.35\, \mathrm{g/cm^3}$ (upper-left prism) 
and $0.4\, \mathrm{g/cm^3}$ (upper-right prism). 
Figure \ref{fig:synthetic_data} shows the gravity disturbance (vertical component of gravitational attraction) 
produced by these sources. The synthetic data are contaminated with additive pseudorandom Gaussian 
noise with zero mean and standard deviation of $0.015$ mGal.
We created $N = 10\,000$ observation points regularly spaced on a grid of $100 \times 100$, on a 
horizontal plane at $z_{1} = -100$ m, and set a grid of equivalent point masses, each one directly beneath each 
observation point, located at depth $z_{0} = 300$ m.

@@

We performed the upward and downward continuations of the simulated gravity data 
(Figure \ref{fig:synthetic_data}) by using the fast equivalent-layer technique 
and our method.
Figure \ref{fig:upward_comparison} shows that the upward-continued gravity data obtained 
by using both methods are in close agreement with those produced by the synthetic 
bodies at $z = XXXX$ m (Figure \ref{fig:upward_comparison}a).
As we can see in Figures \ref{fig:upward_comparison}b and \ref{fig:upward_comparison}c,
the residuals between the upward-continued and true data have their means and standard 
deviations close to zero. 
Figure \ref{fig:downward_comparison} shows similar results obtained by using both 
methods to compute downward continuation of gravity data.
It is important to stress that, although both methods are able to produce a reliable 
upward/downward continuation of gravity data, the computation time spent by our method 
is approximately $1\,500$ times smaller than that of the fast equivalent-layer 
technique \citep{siqueira-etal2017}.

>>>>

We have simulated three sources whose horizontal projections are shown in 
Figure \ref{fig:synthetic_data} as black lines. 
These sources are a sphere with density contrast  
$-1.25\, \mathrm{g/cm^3}$ and two rectangular prisms with density contrasts 
$1.00\, \mathrm{g/cm^3}$ (upper-left prism) 
and $1.30\, \mathrm{g/cm^3}$ (upper-right prism). 
Figure \ref{fig:synthetic_data} shows the gravity disturbance (vertical component of 
gravitational attraction) produced by these sources. 
The synthetic data are contaminated with additive pseudorandom Gaussian 
noise with zero mean and standard deviation of $0.1 \, \mathrm{mGal}$.
The data are computed at $N = 10\,000$ observation points that are regularly spaced on a 
$100 \times 100$ grid, at $z_{1} = -100$ m. 
We have set a grid of equivalent sources, each one directly beneath each 
observation point, located at $z_{0} = 300$ m.

PAREI AQUI

@@

We performed the upward and downward continuations of the simulated gravity data 
(Figure \ref{fig:synthetic_data}) by using the fast equivalent-layer technique 
and our method.
Figure \ref{fig:upward_comparison} shows that the upward-continued gravity data obtained 
by using both methods are in close agreement with those produced by the synthetic 
bodies at $z = -300$ m (Figure \ref{fig:upward_comparison}a).
As we can see in Figures \ref{fig:upward_comparison}b and \ref{fig:upward_comparison}c,
the residuals between the upward-continued and true data have their means and standard 
deviations close to zero. 
Figure \ref{fig:downward_comparison} shows similar results obtained by using both 
methods to compute downward continuation of gravity data.
It is important to stress that, although both methods are able to produce a reliable 
upward/downward continuation of gravity data, the computation time spent by our method 
is approximately $1\,500$ times smaller than that of the fast equivalent-layer 
technique \citep{siqueira-etal2017}.
